Arrows for Parallel Computations

### 2017-12-07 paper/content/conclusion.tex
minor

\section{Conclusion}
\label{sec:conclusion}
Arrows are a generic concept that allows for powerful composition
combinators. To our knowledge we are first to represent
\emph{parallel} computation with Arrows.
% \olcomment{that strange arrows-based robot interaction paper from 1993 or so! clearly discuss in related work} \done
%
Arrows turn out to be a useful tool for composing parallel
programs. We do not have to introduce new monadic types that wrap the
computation. Instead, we use Arrows in the same manner one uses sequential pure functions. Even though we make heavy use of the |ArrowApply| typeclass - which only Arrows that are equivalent to Monads can satisfy - in this paper, we believe that the general idea of an Arrow, the process of doing something - a \emph{computation}, is the perfect fit to use in a library for parallel computation as it allows users to think about parallel programs more as a set of composed computations - like a data-flow graph. Furthermore, our approach allows for a more natural paralellization of any Arrow type (especially regular functions (|->|)), when compared to Monads as we do not have to change anything in order to run them in parallel.
%
This work features multiple parallel backends: the already available parallel Haskell flavours. Parallel Arrows, as presented here, feature an implementation of the |ArrowParallel| type class for GpH Haskell, |Par| Monad, and Eden. With our approach parallel programs can be ported across these flavours with little to no effort. It is quite straightforward to add further backends. 
%
%
Performance-wise, Parallel Arrows are on par with existing parallel Haskells, as they only introduce minor overhead in some of our benchmarks.
%
The benefit is, however, the greatly increased portability of parallel programs.

>>>>

\section{Conclusion}
\label{sec:conclusion}
Arrows are a generic concept that allows for powerful composition
combinators. To our knowledge we are first to represent
\emph{parallel} computation with Arrows.
% \olcomment{that strange arrows-based robot interaction paper from 1993 or so! clearly discuss in related work} \done
%
Arrows turn out to be a useful tool for composing parallel
programs. We do not have to introduce new monadic types that wrap the
computation. Instead, we use Arrows in the same manner one uses sequential pure functions. Even though we make heavy use of the |ArrowApply| typeclass - which only Arrows that are equivalent to Monads can satisfy - in this paper, we believe that the general idea of an Arrow, the process of doing something - a composable \emph{computation}, is the perfect fit to use in a library for parallel computation as it allows users to think about parallel programs more as a set of composed computations - like a data-flow graph. Furthermore, our approach allows for a more natural paralellization of any Arrow type (especially regular functions (|->|)), when compared to Monads as we do not have to change anything in order to run them in parallel.
%
This work features multiple parallel backends: the already available parallel Haskell flavours. Parallel Arrows, as presented here, feature an implementation of the |ArrowParallel| type class for GpH Haskell, |Par| Monad, and Eden. With our approach parallel programs can be ported across these flavours with little to no effort. It is quite straightforward to add further backends. 
%
%
Performance-wise, Parallel Arrows are on par with existing parallel Haskells, as they only introduce minor overhead in some of our benchmarks.
%
The benefit is, however, the greatly increased portability of parallel programs.
